Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
fixed some values in the table; % -> number

% TODO explain tables
\begin{table*}[t]
	\centering
	\caption{My caption}
	\small
	\label{within-subject-table}
	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
		\cline{2-9}
		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Belivability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
		\multicolumn{1}{|c|}{\%} & 96.61\% & \multicolumn{2}{c|}{49.72\%} & 53.67\% & 77.91\% & 79.69\% & 10.61\% & 14.69\% \\ \hline
		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
	\end{tabular}
\end{table*}

@@

		\begin{tabular}{ccccccccccccccccc}

@@

			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{2}{c|}{GPS usage}                                                                                       & \multicolumn{2}{c|}{Traveller type}                                                                                  & \multicolumn{2}{c|}{Companions}                                                                                               & \multicolumn{6}{c|}{Distance}                                                                                                                                                                                                                                                                                                            & \multicolumn{2}{c|}{Visit frequency}                                                                                 \\ \cline{4-17} 
			\multicolumn{1}{c}{}                                 & \multicolumn{1}{c}{}                         & \multicolumn{1}{c|}{}      & \multicolumn{1}{c|}{GPS user}                             & \multicolumn{1}{c|}{non-GPS user}                        & \multicolumn{1}{c|}{Frequent}                             & \multicolumn{1}{c|}{Non-frequent}                        & \multicolumn{1}{c|}{Alone}                                     & \multicolumn{1}{c|}{Not alone}                              & \multicolumn{1}{c|}{0}                                & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{2}                               & \multicolumn{1}{c|}{3}                               & \multicolumn{1}{c|}{4}                               & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{Most}                                 & \multicolumn{1}{c|}{Least}                               \\ \hline
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}60}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}119}         & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}74}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}5}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}8}       & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}18}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}47}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81}          \\ \cline{3-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}33.33\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}57.98\%}     & \multicolumn{1}{c|}{50.83\%}                              & \multicolumn{1}{c|}{47.46\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}55.00\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.22\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}43.66\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}51.56\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}10.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}72.34\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}35.80\%}     \\ \cline{3-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{l|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$\\ p =0.0016\end{tabular}}  & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$\\ p = 0.3953\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 31.812$\\ p \textless0.0001\end{tabular}}  & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$\\ p = 0.0028\end{tabular}}                                                                                                                                                                                                                   & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$\\ p = 0.0001\end{tabular}} \\ \cline{2-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{58}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{57}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}94}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{64}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{46}                                   & \multicolumn{1}{c|}{80}                                  \\ \cline{3-17} 
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{48.28\%}                              & \multicolumn{1}{c|}{56.30\%}                             & \multicolumn{1}{c|}{53.33\%}                              & \multicolumn{1}{c|}{54.39\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}61.70\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89.74\%}        & \multicolumn{1}{c|}{60.00\%}                          & \multicolumn{1}{c|}{25.00\%}                         & \multicolumn{1}{c|}{55.56\%}                         & \multicolumn{1}{c|}{59.15\%}                         & \multicolumn{1}{c|}{50.00\%}                         & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{52.17\%}                              & \multicolumn{1}{c|}{56.25\%}                             \\ \cline{3-17} 
			\multicolumn{1}{|c|}{\multirow{-6}{*}{\rotatebox{90}{Memorability}}} & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$\\ p =0.1992\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$\\ p = 0.4478\end{tabular}}                         & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,  133) = 9.016$\\ p = 0.0013\end{tabular}}        & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$\\ p = 0.4467\end{tabular}}                                                                                                                                                                                                                                             & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$\\ p =  0.3987\end{tabular}}                        \\ \hline
			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{19}                                   & \multicolumn{1}{c|}{67}                                  & \multicolumn{1}{c|}{61}                                   & \multicolumn{1}{c|}{25}                                  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}71}                & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}20}             & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{5}                               & \multicolumn{1}{c|}{13}                              & \multicolumn{1}{c|}{30}                              & \multicolumn{1}{c|}{32}                              & \multicolumn{1}{c|}{1}                               & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}34}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}27}          \\ \cline{3-17} 
			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{68.42\%}                              & \multicolumn{1}{c|}{80.60\%}                             & \multicolumn{1}{c|}{77.05\%}                              & \multicolumn{1}{c|}{80.00\%}                             & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}81.69\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}25.00\%}        & \multicolumn{1}{c|}{80.00\%}                          & \multicolumn{1}{c|}{60.00\%}                         & \multicolumn{1}{c|}{69.23\%}                         & \multicolumn{1}{c|}{90.00\%}                         & \multicolumn{1}{c|}{75.00\%}                         & \multicolumn{1}{c|}{0.00\%}                          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}70.59\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88.89\%}     \\ \cline{3-17} 
			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{c|}{\multirow{-3}{*}{\rotatebox{90}{photo}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$\\ p = 0.2073\end{tabular}}                          & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$\\ p = 0.4947\end{tabular}}                          & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 20.956$\\ p \textless 0.0001\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$\\ p= 0.1709\end{tabular}}                                                                                                                                                                                                                                               & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$\\ p =0.078\end{tabular}}    \\ \cline{2-17} 
			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}39}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}89}          & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}91}           & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}37}          & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}88}                & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}39}             & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}4}       & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}12}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}53}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}49}      & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}6}       & \multicolumn{1}{c|}{33}                                   & \multicolumn{1}{c|}{58}                                  \\ \cline{3-17} 
			\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                        & \multicolumn{1}{c|}{\%}  & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}69.23\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}84.27\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}85.71\%}      & \multicolumn{1}{c|}{\cellcolor[HTML]{ACDDAA}64.86\%}     & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.09\%}           & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}71.79\%}        & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}100.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}75.00\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}84.91\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}79.59\%} & \multicolumn{1}{c|}{\cellcolor[HTML]{FFFFC7}33.33\%} & \multicolumn{1}{c|}{69.70\%}                              & \multicolumn{1}{c|}{81.03\%}                             \\ \cline{3-17} 
			\multicolumn{1}{|l|}{\multirow{-6}{*}{\rotatebox{90}{Believability}}} & \multicolumn{1}{l|}{\multirow{-3}{*}{\rotatebox{90}{video}}} & \multicolumn{1}{c|}{p-val} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$\\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$\\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$\\ p =0.086\end{tabular}}           & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$\\ p = 0.0726\end{tabular}}                                                                                                                                                                                                                    & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$\\ p = 0.1647\end{tabular}}                          \\ \hline
			\multicolumn{1}{|c|}{}                               & \multicolumn{1}{c|}{}                        & \multicolumn{1}{c|}{N}     & \multicolumn{1}{c|}{60}                                   & \multicolumn{1}{c|}{119}                                 & \multicolumn{1}{c|}{120}                                  & \multicolumn{1}{c|}{59}                                  & \multicolumn{1}{c|}{74}                                        & \multicolumn{1}{c|}{20}                                     & \multicolumn{1}{c|}{5}                                & \multicolumn{1}{c|}{8}                               & \multicolumn{1}{c|}{18}                              & \multicolumn{1}{c|}{71}                              & \multicolumn{1}{c|}{67}                              & \multicolumn{1}{c|}{10}                              & \multicolumn{1}{c|}{47}                                   & \multicolumn{1}{c|}{81}                                  \\ \cline{3-17} 

>>>>

% TODO explain tables
\begin{table*}[t]
	\centering
	\caption{My caption}
	\small
	\label{within-subject-table}
	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
		\cline{2-9}
		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Belivability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
		\multicolumn{1}{|c|}{\%} & 0.97 & \multicolumn{2}{c|}{0.50} & 0.54 & 0.78 & 0.80 & 0.11 & 0.15 \\ \hline
		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
	\end{tabular}
\end{table*}

@@

\begin{tabular}{ccc|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}

@@

 &  &  & \multicolumn{2}{c|}{GPS usage} & \multicolumn{2}{c|}{Traveller type} & \multicolumn{2}{c|}{Accompany} & \multicolumn{6}{c|}{Distance} & \multicolumn{2}{c|}{Visit frequency} \\ \cline{4-17} 
 &  &  & GPS user & non-GPS user & Frequent & Non-frequent & Alone & Not alone & 0 & 1 & 2 & 3 & 4 & 5 & Most & Least \\ \hline
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 60} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 119} & 120 & 59 & 74 & 11 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 5} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 8} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 18} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 71} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 64} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 10} & \cellcolor[HTML]{ACDDAA}47 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 81} \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.58} & 0.51 & 0.47 & 1.00 & 1.00 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 1.00} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.10} & \cellcolor[HTML]{ACDDAA}0.72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.36} \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 8.734$ \\ p =0.0016\end{tabular}}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.071$ \\ p = 0.3953\end{tabular}} & \multicolumn{2}{c|}{N/A} & \multicolumn{6}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} \begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179 ) = 18.106$ \\ p = 0.0028\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1,128) = 14.458$ \\ p = 0.0001\end{tabular}} \\ \cline{2-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 58 & 119 & 120 & 57 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 94} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 39} & 5 & 8 & 18 & 71 & 64 & 10 & 46 & 80 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.48 & 0.56 & 0.53 & 0.54 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.62} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.90} & 0.60 & 0.25 & 0.56 & 0.59 & 0.50 & 0.60 & 0.52 & 0.56 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Memorability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 0.713$ \\ p =0.1992\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.017$ \\ p = 0.4478\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 9.016$ \\ p = 0.0013\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 4.754$ \\ p = 0.4467\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.066$ \\ p = 0.3987\end{tabular}} \\ \hline
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 19 & 67 & 61 & 25 & \cellcolor[HTML]{ACDDAA}71 & \cellcolor[HTML]{ACDDAA}11 & 5 & 5 & 13 & 30 & 32 & 1 & \cellcolor[HTML]{FFFFC7}34 & \cellcolor[HTML]{FFFFC7}27 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & \cellcolor[HTML]{FFFFC7}0.71 & \cellcolor[HTML]{FFFFC7}0.89 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.666$ \\ p = 0.2073\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 86) = 0.000$ \\ p = 0.4947\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 82) = 5.137$ \\ p = 0.0117\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 86) = 7.745$ \\ p= 0.1709\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 61) = 2.013$ \\ p =0.078\end{tabular}} \\ \cline{2-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}39 & \cellcolor[HTML]{ACDDAA}89 & \cellcolor[HTML]{ACDDAA}91 & \cellcolor[HTML]{ACDDAA}37 & \cellcolor[HTML]{FFFFC7}88 & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}4 & \cellcolor[HTML]{FFFFC7}12 & \cellcolor[HTML]{FFFFC7}53 & \cellcolor[HTML]{FFFFC7}49 & \cellcolor[HTML]{FFFFC7}6 & 33 & 58 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & \cellcolor[HTML]{FFFFC7}0.84 & \cellcolor[HTML]{FFFFC7}0.72 & \cellcolor[HTML]{FFFFC7}1.00 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.75 & \cellcolor[HTML]{FFFFC7}0.85 & \cellcolor[HTML]{FFFFC7}0.80 & \cellcolor[HTML]{FFFFC7}0.33 & 0.70 & 0.81 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Belivability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & 60 & 119 & 120 & 59 & 74 & 11 & 5 & 8 & 18 & 71 & 67 & 10 & 47 & 81 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.13 & 0.92 & 0.13 & 0.07 & 0.12 & 0.18 & 0.20 & 0.38 & 0.06 & 0.07 & 0.13 & 0.10 & 0.15 & 0.10 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{\multirow{-3}{*}{photo}} & p-val & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.338$ \\ p = 0.2804\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 0.828$\\ p = 0.1814\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 94) = 0.071$ \\ p = 0.3948\end{tabular}} & \multicolumn{6}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 179) = 8.131$ \\ p = 0.1492\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128)= 0.32$ \\ p = 0.2858\end{tabular}} \\ \cline{2-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & N & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 58} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 119} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 120} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 57} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 94} & \cellcolor[HTML]{FFFFC7}39 & \cellcolor[HTML]{FFFFC7}5 & \cellcolor[HTML]{FFFFC7}8 & \cellcolor[HTML]{FFFFC7}18 & \cellcolor[HTML]{FFFFC7}70 & \cellcolor[HTML]{FFFFC7}66 & \cellcolor[HTML]{FFFFC7}10 & 46 & 80 \\ \cline{3-17} 
\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & \cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} 0.13} & \cellcolor[HTML]{FFFFC7}0.26 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.00 & \cellcolor[HTML]{FFFFC7}0.11 & \cellcolor[HTML]{FFFFC7}0.10 & \cellcolor[HTML]{FFFFC7}0.20 & \cellcolor[HTML]{FFFFC7}0.40 & 0.11 & 0.18 \\ \cline{3-17} 
\multicolumn{1}{|c|}{\multirow{-6}{*}{Desirability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 177) = 7.319$ \\ p = 0.0034\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 179) = 9.754$\\ p = 0.0009\end{tabular}}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}{\color[HTML]{333333} \begin{tabular}[c]{@{}c@{}}$\chi^2(1, 133) = 2.443$ \\ p = 0.059\end{tabular}}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 177) = 10.084$ \\ p= 0.0729\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 126) = 0.552$ \\ p = 0.2288\end{tabular}} \\ \hline
